---
title: "Linear Regression"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Using lm() Function in R

lm() function in R is a linear model function, used for linear regression analysis. 


lm(formula, data, ...)




Here is the data I will use.
sample file: train data from Kaggle Walmart data set


```{r setup, include=FALSE}
train <- read.csv("kaggle_walmart_train.csv")
head(train)
```

below is scatter plot of train data.
for draw scatter plot, set the data using group_by function.


```{r setup, include=FALSE}
library(dplyr)
train_groupby<- group_by(train, Store) %>% summarise(Weekly_Sales = mean(Weekly_Sales))


with(train_groupby,
     plot(Store, Weekly_Sales, asp=1,
          xlab="Store",
          ylab="Weekly_sales",
          main="plot of weekly_sales & store"))

```






```{r setup, include=FALSE}
result <- lm(Weekly_Sales~Store, data=train)
attributes(result)

```
result라는 객체는 lm클래스에 속하며, 12개의 결과값을 가지고 있습니다. 
There are 12 values. 

### Coefficients 

```{r setup, include=FALSE}
result$coefficients

```
These are intercept and slope of linear which we want to get.  







